\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Rev 1\\\progname}

\author{\authname}

\date{}


\begin{document}

\maketitle


\section{Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 9\\
Buu Ha & 9\\
Rishi Vaya & 9\\
Diaomnd Ahuja & 9\\
Dhruv Cheemakurti & 9\\
Umang Rajkarnikar & 8\\
\bottomrule
\end{tabular}
\end{table}

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Buu Ha & 1\\
Rishi Vaya & 0\\
Diaomnd Ahuja & 0\\
Dhruv Cheemakurti & 0\\
Umang Rajkarnikar & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 683 & 100\% \\
Buu Ha & 193 & 28.2\% \\
Rishi Vaya & 92 & 13.5\% \\
Diamond Ahuja & 80 & 11.7\% \\
Dhruv Cheemakurti & 126 & 18.4\% \\
Umang Rajkarnikar & 192 & 28.1\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Contributions}

Quinn - Worked primarily on satellite information, including tracking, calculating overpasses, and generating polar plot displays. Worked on initial design, dynamic routing of users, satellites, and schedules, and implemented a majority ( $\geq$ 60\%) of the final front-end code. In addition, led stakeholder meetings, and led front-end efforts with the help of Diamond and Dhruv.
\\
\\
Diamond - My role in the project centered on frontend development, enhancing the Logs page styling, implemented a date filter on the Scheduler and Next Week's passes page and created a page for managing satellite commands. In the initial phases, I collaborated with Umang to establish a websocket connection for direct communication with the ground station. In addition, I was responsible for recording meeting minutes during our discussions.
\\
\\
Rishi - Primarily worked on the endpoints of the application to create, update and delete entries from the mongoDB database. Created function required for front-end implementation. Collaborated with other team mates to updates database schemas. Additionally, created back-end test cases and implemented endpoint protection.
\\
\\
Umang - Primarily worked on building the backend of the application. This included creating endpoints to manage satellite and schedules in the database. Also, worked on establishing a secure socket connection for direct communication with the ground station. In addition, I implemented the terminal interface which allows users to interact with the socket connection directly from the frontend. Lastly, I led the production deployment of both the frontend and backend code.
\\
\\ 
Dhruv - My role in the project was mainly front-end focused. I was tasked with developing and enhancing the UI flow for Schedular page, Edit Schedules and Satellites of Interest. Also worked on adding commands feature where it allows the admin to add new command permissions for each operator. I was working with Quinn and Diamond on the front-end side mainly. Additionally, helped implement some of the UI changes from testing demos with stakeholders which contributes to a good chunk of the final-front end code. 

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Buu Ha & 66 & 8 \\
Rishi Vaya & 0 & 5 \\
Diamond Ahuja & 19 & 1 \\
Dhruv Cheemakurti & 0 & 1 \\
Umang Rajkarnikar & 14 & 22 \\
\bottomrule
\end{tabular}
\end{table}


\end{document}